Extreme Digitisation For Ground-Based Cosmic Microwave Background Experiments

### 2018-12-21 digitisation.tex
app

\def\arraystretch{1.3}
\begin{table*}[tbh]
\begin{center}
\caption{\label{tab:extranoiseoof} \changed{Fractional Noise Increase Due To Digitisation - $1/f$ Detector Noise}}
\small
\begin{tabular}{c c c c c}
Hits Per Pixel & Channel & 1 Bit & 2 Bit & 3 Bit \\
\hline
\hline
\multirow{3}{*}{8,000}  & TT  & $ 0.231 \pm 0.017 $  & $ 0.0584 \pm 0.0052 $  & $ 0.0159 \pm 0.0022 $ \\
& EE  & $ 0.250 \pm 0.012 $  & $ 0.0641 \pm 0.0043 $  & $ 0.0177 \pm 0.0019 $ \\
& BB  & $ 0.245 \pm 0.021 $  & $ 0.0623 \pm 0.0067 $  & $ 0.0169 \pm 0.0032 $ \\
\hline
\multirow{3}{*}{102,400}  & TT  & $ 0.235 \pm 0.014 $  & $ 0.0597 \pm 0.0042 $  & $ 0.0166 \pm 0.0019 $ \\
& EE  & $ 0.2503 \pm 0.0091 $  & $ 0.0636 \pm 0.0042 $  & $ 0.0174 \pm 0.0016 $ \\
& BB  & $ 0.249 \pm 0.024 $  & $ 0.0641 \pm 0.0069 $  & $ 0.0178 \pm 0.0025 $ \\
\hline
\multirow{3}{*}{1,024,000}  & TT  & $ 0.238 \pm 0.013 $  & $ 0.0601 \pm 0.0046 $  & $ 0.0168 \pm 0.0019 $ \\
& EE  & $ 0.2502 \pm 0.0078 $  & $ 0.0630 \pm 0.0039 $  & $ 0.0173 \pm 0.0019 $ \\
& BB  & $ 0.2499 \pm 0.0095 $  & $ 0.0636 \pm 0.0049 $  & $ 0.0177 \pm 0.0019 $ \\
\hline
\multirow{3}{*}{Average}  & TT  & $ 0.2346 \pm 0.0020 $  & $ 0.0594 \pm 0.0020 $  & $ 0.0164 \pm 0.0020 $ \\
 & EE  & $ 0.2503 \pm 0.0018 $  & $ 0.0636 \pm 0.0018 $  & $ 0.0175 \pm 0.0018 $ \\
 & BB  & $ 0.2480 \pm 0.0025 $  & $ 0.0633 \pm 0.0025 $  & $ 0.0175 \pm 0.0025 $ \\
\end{tabular}
\tablecomments{ 
\changed{(TABLE HAS BEEN CHANGED) Fractional addition to the map noise level, $\Delta \sigma / \sigma$, due to one-, two-, and three-bit digitisation for $1/f$ detector noise with $1\sigma$ confidence intervals. As in the white noise case, we observe no significant trend between temperature and polarisation or for different depths of observation. We note that, even assuming a more realistic noise profile, three-bit digitisation only leads to a percent-level increase in the map noise level.}
} \normalsize
\end{center}
\end{table*}

@@

\changed{ where we sum over all output levels of both timestreams $(1, 2)$ and $P$ denotes the probability of an output level occurring. For current-generation CMB experiments it is common to draw from $>10^5$ samples to obtain an estimate of a map pixel. This corresponds to adding many noise realisation on top of the same signal, $\mu$. 
The central limit theorem ensures that the amplitude probability distribution function of the noise in each pixel is Gaussian. 
The probabilities $P$ in the above expression can therefore be expressed as integrals over normal distributions, $p(\xi)$, with mean zero and standard deviation $\sigma$.}

@@

\changed{because} $\psi_{N-i}^{k,n} = (-1)^{k} \psi_{i}^{k,n}$. \changed{Since ground-based CMB experiments operate at low signal-to-noise we calculate the leading order terms of the signal, $\mu$, in equation \ref{eq:dcompleteklsum}. We split the sum over $k, l$ in said equation as follows:}

>>>>

\def\arraystretch{1.3}
\begin{table*}[tbh]
\begin{center}
\caption{\label{tab:extranoiseoof} \changed{Fractional Noise Increase Due To Digitisation - $1/f$ Detector Noise}}
\small
\begin{tabular}{c c c c c}
Hits Per Pixel & Channel & 1 Bit & 2 Bit & 3 Bit \\
\hline
\hline
\multirow{3}{*}{8,000}  & TT  & $ 0.231 \pm 0.017 $  & $ 0.0584 \pm 0.0052 $  & $ 0.0159 \pm 0.0022 $ \\
& EE  & $ 0.250 \pm 0.012 $  & $ 0.0641 \pm 0.0043 $  & $ 0.0177 \pm 0.0019 $ \\
& BB  & $ 0.245 \pm 0.021 $  & $ 0.0623 \pm 0.0067 $  & $ 0.0169 \pm 0.0032 $ \\
\hline
\multirow{3}{*}{102,400}  & TT  & $ 0.235 \pm 0.014 $  & $ 0.0597 \pm 0.0042 $  & $ 0.0166 \pm 0.0019 $ \\
& EE  & $ 0.2503 \pm 0.0091 $  & $ 0.0636 \pm 0.0042 $  & $ 0.0174 \pm 0.0016 $ \\
& BB  & $ 0.249 \pm 0.024 $  & $ 0.0641 \pm 0.0069 $  & $ 0.0178 \pm 0.0025 $ \\
\hline
\multirow{3}{*}{1,024,000}  & TT  & $ 0.238 \pm 0.013 $  & $ 0.0601 \pm 0.0046 $  & $ 0.0168 \pm 0.0019 $ \\
& EE  & $ 0.2502 \pm 0.0078 $  & $ 0.0630 \pm 0.0039 $  & $ 0.0173 \pm 0.0019 $ \\
& BB  & $ 0.2499 \pm 0.0095 $  & $ 0.0636 \pm 0.0049 $  & $ 0.0177 \pm 0.0019 $ \\
\hline
\multirow{3}{*}{Average}  & TT  & $ 0.2346 \pm 0.0020 $  & $ 0.0594 \pm 0.0020 $  & $ 0.0164 \pm 0.0020 $ \\
 & EE  & $ 0.2503 \pm 0.0018 $  & $ 0.0636 \pm 0.0018 $  & $ 0.0175 \pm 0.0018 $ \\
 & BB  & $ 0.2480 \pm 0.0025 $  & $ 0.0633 \pm 0.0025 $  & $ 0.0175 \pm 0.0025 $ \\
\end{tabular}
\tablecomments{ 
\changed{Fractional addition to the map noise level, $\Delta \sigma / \sigma$, due to one-, two-, and three-bit digitisation for $1/f$ detector noise with $1\sigma$ confidence intervals. As in the white noise case, we observe no significant trend between temperature and polarisation or for different depths of observation. We note that, even assuming a more realistic noise profile, three-bit digitisation only leads to a percent-level increase in the map noise level.}
} \normalsize
\end{center}
\end{table*}

@@

\changed{ where we sum over all output levels of both timestreams $(1, 2)$ and $P$ denotes the probability of an output level occurring. 
The final estimate of the value in a map pixel is frequently based on $>10^5$ TOD samples in current CMB experiments, and this number will increase with the number of detectors for future experiments. 
This can is equivalent to have many noise realisations on top of the same signal, $\mu$. 
Given the number of samples, the central limit theorem ensures that the amplitude probability distribution function of the noise in each pixel is Gaussian. 
The probabilities $P$ in the above expression can therefore be expressed as integrals over normal distributions, $p(\xi)$, with mean zero and standard deviation $\sigma$.}

@@

\changed{because} $\psi_{N-i}^{k,n} = (-1)^{k} \psi_{i}^{k,n}$. \changed{Since the TOD of ground-based CMB experiments has low signal-to-noise, we calculate the leading order terms of the signal, $\mu$, in equation \ref{eq:dcompleteklsum}. We split the sum over $k, l$ in said equation as follows:}
